% This is main.tex, a sample paper demonstrating the use of the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
% 
\documentclass[runningheads]{llncs}
\usepackage[a4paper,left=3cm,right=3cm,top=4cm,bottom=4cm,bindingoffset=5mm]{geometry}
%
% ---- Packages ----
%
\usepackage{graphicx} % enhanced support for graphics
\usepackage{url} % add macros for handling URLs in text
\usepackage[nohyperlinks,nolist]{acronym} % abbreviation utilities
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{float}
\usepackage{pgfplots}
\pgfplotsset{width=10cm,compat=1.16}
% TODO: add more packages below if necessary
%
% ---- Acronyms ----
%
\begin{acronym}
\acro{rq}[RQ]{Research Question}
\acro{NLP}[NLP]{Natural Language Processing}
\end{acronym}
%
% ---- Begin Document ----
%
\begin{document}
\title{NLP-Based Manual Test Case Selection}
\author{Marius Bosler}
\institute{Seminar: Software Quality\\
Advisor: Roland Würsching\\
Technical University of Munich\\
\email{marius.bosler@tum.de}}
%
\maketitle % typeset the header of the contribution
%
% ---- Abstract ----
%
\begin{abstract}
Even though there have been many advancements in recent years, a significant portion of software testing still needs to be conducted manually. This means that, with each software release requiring numerous manual tests, a considerable amount of time is spent executing these tests. Meanwhile, many of these tests tend to overlap regarding bug detection, which could be avoided if a method were found to execute only the necessary number of tests, as multiple tests may detect the same bug. One solution using this fact is to cluster tests based on the language used in their descriptions, in this case only their test steps. Then, by selecting only a subset of all tests based on that clustering, we get tests that are dissimilar in their language. This results in a significantly larger bug coverage. When selecting 50\% of tests with this approach, we cover 72.5\% of bug tickets, compared to 53\% with a more naive approach. These results are promising, especially considering only so little information was used to find test similarity. 


\keywords{Test Selection, Natural Language Processing, Clustering}
\end{abstract}
%
% ---- Text Parts ----
%
\input{text/01_introduction}
\input{text/02_related_work.tex}
\input{text/03_methodology.tex}
\input{text/04_evaluation.tex}
\input{text/05_discussion.tex}
\input{text/06_threats_to_validity.tex}
\input{text/07_conclusion.tex}
%
% ---- Bibliography ----
%
\bibliographystyle{splncs04}
en%
\end{document}
